The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-12 Paper.Rmd
skewness plot axis labels fixed
minor change

\begin{figure}[!h]
\textbf{ \hspace{6 cm} (A) \hspace{6 cm} (B)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf}\\
\end{center}
\vspace{0.2 cm}
\textbf{ \hspace{6 cm} (C) \hspace{6 cm} (D)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf}
\caption{Skewness of spatially averaged green spruce aphid abundance $(A)$, leaf-curling plum 
aphid first flight dates $(B)$, \emph{Ceratium furca} abundance $(C)$, and methane-flux
$(D)$ time series compared to an multivariate 
N-copula null hypothesis. Red dots are empirical 
skewnesses; see text 
and Appendix \ref{SM-Surrog_multi} for details of the null hypothesis. Results show a 
tendency for skewness of the spatial average to be affected as hypothesized 
by tail dependence. \label{fig_skewness_spearman}}
\end{center}
\end{figure}
<!--***DAN: Shya, please replace the x axis label by "Skewness" and the y-axis label
by "Frequency"-->

@@

We used our four multivariate data sets : aphid-count data, aphid-first flight data, plankton data and methane-flux data, to compute skewness of spatially averaged data. We carried out the analysis mentioned in the concepts above for spearman preserving surrogates, with aphid abundance and aphid first flight date data for all 20 aphid species and plankton abundance data for all 22 plankton species. In each study, we got $>5\%$ positive results which gave us confidence in validating significantly different skewness for asymmetric copula than Normal. For example, Figure \ref{fig_skewness_spearman} represents the results for each data set with Spearman correlation preserving surrogates. Figure \ref{fig_skewness_spearman}(A) showed that averaged skewness (indicated by red dot) was much lower than expected if the green-spruce aphid count data came from a normal copula. In that example, $p$ value was denoted by the fraction of surrogate-skewness which were lower than the averaged skewness of the given data. As $p<0.05$, we rejected $H_{0}$ in support of significantly stronger lower tail dependence which was also consistent with the nonparametric analysis and model fitting results (see first column of Table \ref{tab_multivar_summary}). On the other hand, Figure \ref{fig_skewness_spearman}(B) demonstrated that averaged skewness was significantly higher than expected if the leaf-plum curling aphid first flight data came from a normal copula, which was also confirmed by upper-tail dependence results from model selection and nonparametric results (see second column of Table \ref{tab_multivar_summary}). Figure \ref{fig_skewness_spearman}(C) showed that averaged skewness was lower than expected if the plankton data came from a normal copula. Our previous results on nonparametric analysis and model fitting also supported lower tail dependence (see third column of Table \ref{tab_multivar_summary}). But, as $p>0.05$, we could not reject $H_{0}$ in that case. Finally, for methane-flux data, the averaged skewness was found significantly lower in comparison to its Normal surrogates (Figure \ref{fig_skewness_spearman} D). 
<!--We found the same result with all data sets when we repeated our simulation with Kendall correlation preserving surrogates (see Fig. \ref{SM-fig_skewness_kendall}). Now we did only with spearman preserving to handle ties and +ve semidefinite case-->

>>>>

\begin{figure}[!h]
\textbf{ \hspace{6 cm} (A) \hspace{6 cm} (B)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf}\\
\end{center}
\vspace{0.2 cm}
\textbf{ \hspace{6 cm} (C) \hspace{6 cm} (D)} \\
\vspace{-0.1 cm}
\begin{center}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf}
\includegraphics[width=5.5 cm]{./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf}
\caption{Skewness of spatially averaged green spruce aphid abundance $(A)$, leaf-curling plum 
aphid first flight dates $(B)$, \emph{Ceratium furca} abundance $(C)$, and methane-flux
$(D)$ time series compared to an multivariate 
N-copula null hypothesis. Black dots are empirical 
skewnesses; see text 
and Appendix \ref{SM-Surrog_multi} for details of the null hypothesis. Results show a 
tendency for skewness of the spatial average to be affected as hypothesized 
by tail dependence. \label{fig_skewness_spearman}}
\end{center}
\end{figure}
<!--***DAN: Shya, please replace the x axis label by "Skewness" and the y-axis label
by "Frequency"
***Shya: Done.-->

@@

We used our four multivariate data sets : aphid-count data, aphid-first flight data, plankton data and methane-flux data, to compute skewness of spatially averaged data. We carried out the analysis mentioned in the concepts above for spearman preserving surrogates, with aphid abundance and aphid first flight date data for all 20 aphid species and plankton abundance data for all 22 plankton species. In each study, we got $>5\%$ positive results which gave us confidence in validating significantly different skewness for asymmetric copula than Normal. For example, Figure \ref{fig_skewness_spearman} represents the results for each data set with Spearman correlation preserving surrogates. Figure \ref{fig_skewness_spearman}(A) showed that averaged skewness (indicated by black dot) was much lower than expected if the green-spruce aphid count data came from a normal copula. In that example, $p$ value was denoted by the fraction of surrogate-skewness which were lower than the averaged skewness of the given data. As $p<0.05$, we rejected $H_{0}$ in support of significantly stronger lower tail dependence which was also consistent with the nonparametric analysis and model fitting results (see first column of Table \ref{tab_multivar_summary}). On the other hand, Figure \ref{fig_skewness_spearman}(B) demonstrated that averaged skewness was significantly higher than expected if the leaf-plum curling aphid first flight data came from a normal copula, which was also confirmed by upper-tail dependence results from model selection and nonparametric results (see second column of Table \ref{tab_multivar_summary}). Figure \ref{fig_skewness_spearman}(C) showed that averaged skewness was lower than expected if the plankton data came from a normal copula. Our previous results on nonparametric analysis and model fitting also supported lower tail dependence (see third column of Table \ref{tab_multivar_summary}). But, as $p>0.05$, we could not reject $H_{0}$ in that case. Finally, for methane-flux data, the averaged skewness was found significantly lower in comparison to its Normal surrogates (Figure \ref{fig_skewness_spearman} D). 
<!--We found the same result with all data sets when we repeated our simulation with Kendall correlation preserving surrogates (see Fig. \ref{SM-fig_skewness_kendall}). Now we did only with spearman preserving to handle ties and +ve semidefinite case-->
